Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
paper final draft

```{r}

#| label: fig-candidate_fixed
#| fig-cap: "Candidate Fixed Effects in Hierachical Bayesian Model" 
#| echo: false
#| warning: false
#| message: false

# Load necessary libraries
library(ggplot2)
library(readr)
library(here)

# Load the candidate fixed effect data
candidate_data <- read_csv(here("data", "02-analysis_data", "candidate_fixed_effect.csv"))

>>>>

```{r}
#| label: fig-candidate_fixed
#| fig-cap: "Candidate Fixed Effects in Hierachical Bayesian Model" 
#| echo: false
#| warning: false
#| message: false
#| fig-height: 5
#| fig-width: 6

# Load the candidate fixed effect data
candidate_data <- read_csv(here("data", "02-analysis_data", "candidate_fixed_effect.csv"), show_col_types = FALSE)
